
\begin{Group}{Whiskys}

\Entry{Ardbeg Corryvreckan}{40 kr}
\Expl{This baby packs a serious punch! It is a heavily smoky and peated islay single malt with a 57.1\% alcohol content that will warm your soul. Despite it's impressive potency it still has a deep complexity of flavours with a note of earth and charcuteries, subtle hints of citrus, dried herbs and anise followed by an end-note of walnuts.} 


\Entry{Auchentoshan 12y}{30 kr}
\Expl{"Smooth and sweet with hints of tangerine and lime." - official webpage. 
Tangerine might be more precise than most would be able to  discern, but it is indeed a quite subtle and fruity whisky with a slight nuttiness to the after-taste.}


\Entry{Jura Superstition}{35 kr}
\Expl{A very smooth whisky from the Scottish isle of jura. A light touch of smoke but delicate in nature and does not lack in flavour. Overtones of dried fruit, nuts, orange and vanilla. This gentle yet complex whisky is an excellent first whisky of the evening, or a good first for the ones yet uninitiated to the fine world of whiskys. }


\Entry{Lagavulin 16y}{35 kr}
\Expl{ A very thick and rich islay whiskey. A massive mouthful of malt and sherry with hints of fruity sweetness, Powerful peaty smokiness with lingering notes of oak. }

\Entry{Laphroaig Quarter Cask}{30 kr}
\Expl{Full bodied, malty and very smokey islay. The whisky has been double matured, first in oak barrels previously used for American bourbon, then in smaller quarter casks. This process ensures strong overtones of wood but it also has a slight sweetness and a lingering after-taste of smoke and spices. }

\Entry{Laphroaig 18y}{40 kr}
\Expl{"An instant warming tang of smoke fades into smooth floral scents, which blends seamlessly into an oaky nuttiness and leaves a lasting sweetness on the taste. With a touch of water, the peaty warmth fills the mouth but does not overshadow the sweet chocolate smoothness. This is balanced by the rich toffee taste and slowly fades into a delicate hint of heather and peat smoke." - official webpage.
I quote this, not due to laziness but because i agree and cannot write it half as elegant myself without sounding douchey. }


\Entry{Oban}{30 kr}
\Expl{Medium-bodied of light smokiness with an earthy feeling to it, a tangible alcohol punch, oakyness from the barrel and light spray of sea salt with a hint of toffee in the finish. One of the classical islays that should not be overlooked.}

\Entry{Talisker 10y}{25 kr}
\Expl{A smokey, classical, islay whiskey with subtle notes of orange, honey and dark chocolate.}

\end{Group}


%========================================================================================%
%        								RUM												 %
%========================================================================================%

\begin{Group}{Rums}

\Entry{Ron Zacapa}{35 kr}
\Expl{This beautifully smooth and deep rum is a blend of rums aged between 6 and 23 years. The blend is then further aged in whiskey, sherry and wine barrels in the Guatemalan highlands. The result is a deeply golden rum, sweet but not overpoweringly so, with a complexity that few of the rums or whiskys served here can compete with.} 

\Entry{The Kraken}{20 kr}
\Expl{Named for its colour that allegedly resembles the ink of the mighty Kraken (yes, it's american...) this unusually spiced rum is highly appealing to anyone with a sweet tooth. It is very smooth with strong flavours of almond, cinnamon and sweet licorice. It is extraordinarily sweet but remarkably easy to drink. While not quite representative of the world of rums I still bid you to try it as I believe that it will be well received by many.}

\end{Group}
